Channel Shaping Using Reconfigurable Intelligent Surfaces: From Diagonal to Beyond

### 2024-02-17 main.tex
:pencil: Channel singular redistribution

		\begin{corollary}[upper bound on the sum of first $k$ singular values to the power of $p$]
			\begin{equation}
				\sum_{n=1}^k \sigma_n^p(\mathbf{H}) \le \sum_{n=1}^k \sigma_n^p(\mathbf{H}_\mathrm{B}) \sigma_n^p(\mathbf{H}_\mathrm{F}), \quad p > 0.
				\label{iq:sv_bound_fc_power}
			\end{equation}
			When $k = N'$ and $p = 2$, \eqref{iq:sv_bound_fc_power} suggests the channel power is upper bounded by the sum of (sorted) element-wise power product of backward and forward subchannels.
		\end{corollary}

		\begin{remark}
			Interestingly, \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when $\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}$.
			We thus conclude the off-diagonal entries can enhance the capabilities of
			\begin{itemize}
				\item subspace alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:scattering_fc} fully align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
				\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximal in rearrangement inequality.
			\end{itemize}
		\end{remark}

@@

		\begin{proposition}\label{pp:power}
			Start from any $\mathbf{\Theta}^{(0)} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, the sequence
			\begin{equation}
				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
			\end{equation}
			converges to a stationary point of \eqref{op:power_passive}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are the left and right compact singular matrix of
			\begin{equation}
				\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathrm{diag}\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
			\end{equation}
		\end{proposition}

@@

	\begin{subsection}{Channel Singular Values Redistribution}
		\begin{subsubsection}{Pareto Frontier}
			\begin{figure}[!t]
				\centering
				\subfloat[$2 \times 32 \times 2$ (no direct)\label{fg:singular_pareto_sx32_nd}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_pareto_sx32_nd.tex}
					}
				}
				\subfloat[$2 \times 32 \times 2$\label{fg:singular_pareto_sx32}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_pareto_sx32.tex}
					}
				}
				\\
				\subfloat[$2 \times 64 \times 2$\label{fg:singular_pareto_sx64}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_pareto_sx64.tex}
					}
				}
				\subfloat[$2 \times 128 \times 2$\label{fg:singular_pareto_sx128}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_pareto_sx128.tex}
					}
				}
				\caption{Pareto frontiers of 2T2R channel singular values reshaped by a \gls{ris}.}
				\label{fg:singular_pareto}
			\end{figure}
			% Fig. \ref{fg:singular_pareto} shows the Pareto frontiers of channel singular values reshaped by \gls{bd}-\gls{ris}.
			Fig. \ref{fg:singular_pareto} shows the Pareto singular values of a 2T2R \gls{mimo} reshaped by a \gls{ris}.
			When the direct link is absent, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices since $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$.
			We observe that the smallest singular value is enhanced up to \num{2e-4} by diagonal \gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
			When the direct link is present, the region shape depends heavily on the relative channel strength.
			In Fig. \subref*{fg:singular_pareto_sx32}, a 32-element \gls{ris} cannot compensate the \qty{35}{dB} direct-indirect power imbalance and results in a limited range of singular values.
			The achievable regions are thus symmetric around the direct point.
			Interestingly, the shape evolves from oval to square as the group size $L$ increases, which suggests that \gls{bd}-\gls{ris} can achieve a better tradeoff in subchannel manipulation.
			As the number of scattering elements $N_\mathrm{S}$ increases, the dynamic range of singular values is widened and the achievable region becomes more trapezoidal.
			It is also worth noticing in Fig. \subref*{fg:singular_pareto_sx128} that the equivalent channel can be completely nulled by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} and the importance of in-group connections.
		\end{subsubsection}

		\begin{subsubsection}{Analytical and Numerical Results}
			\begin{figure}[!t]
				\centering
				\subfloat[$4 \times 32 \times 4$ (rank-1)\label{fg:singular_bound_rank1_sx32}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_bound_rank1_sx32.tex}
					}
				}
				\subfloat[$4 \times 64 \times 4$ (rank-1)\label{fg:singular_bound_rank1_sx64}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_bound_rank1_sx64.tex}
					}
				}
				\\
				\subfloat[$4 \times 128 \times 4$ (rank-2)\label{fg:singular_bound_rank2_sx128}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_bound_rank2_sx128.tex}
					}
				}
				\subfloat[$4 \times 256 \times 4$ (rank-4)\label{fg:singular_bound_rank4_sx256}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_bound_rank4_sx256.tex}
					}
				}
				\caption{
					Achievable channel singular values: analytical bounds (green lines) and numerical optimization results (blue and red bars).
					`D' means diagonal \gls{ris} and `BD' means fully-connected \gls{bd}-\gls{ris}.
					`rank-$k$' refers to the forward channel.
				}
				\label{fg:singular_bound}
			\end{figure}
			Fig. \ref{fg:singular_bound} illustrates the analytical bounds in Proposition \ref{pp:rank_deficient} and the numerical results obtained by solving problem \eqref{op:pareto} with $\rho_n = \pm 1$ and $\rho_{n'} = 0$, $\forall n' \ne n$.
			Here we assme a rank-$k$ forward channel without loss of generality.
			When the \gls{ris} is in the vicinity of the transmitter, Figs. \subref*{fg:singular_bound_rank1_sx32} and \subref*{fg:singular_bound_rank1_sx64} show that the achievable channel singular values indeed satisfy Corollary \ref{co:los}, namely $\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T})$, $\sigma_2(\mathbf{T}) \le \sigma_2(\mathbf{H}) \le \sigma_1(\mathbf{T})$, etc.
			We also observe that \gls{bd}-\gls{ris} can approach those bounds better than diagonal \gls{ris} especially for a small $N_\mathrm{S}$.
			% Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} where the forward channel is rank-2.
			Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} where the forward channel is rank-2.
			As expected from Corollary \ref{co:extreme}, the largest 2 singular values are unbounded above and the smallest 2 singular values can be suppressed to zero (with a sufficiently large \gls{ris}).
			Proposition \ref{pp:rank_deficient} also predicts the fact that $\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T})$, $\sigma_2(\mathbf{H}) \ge \sigma_2(\mathbf{T})$, $\sigma_3(\mathbf{H}) \le \sigma_1(\mathbf{T})$, and $\sigma_4(\mathbf{H}) \le \sigma_2(\mathbf{T})$.
			Finally, Fig. \subref*{fg:singular_bound_rank4_sx256} confirms there are no extra bounds when both forward and backward channels are full-rank.
			This is because in \eqref{eq:auxiliary_matrix} the compact singular matrices $\mathbf{V}_\mathrm{F}$ and $\mathbf{U}_\mathrm{F}$ become unitary such that $\mathbf{T}=\mathbf{0}$.
			The numerical results are consistent with the analytical bounds, and we also conclude that the advantage of \gls{bd}-\gls{ris} over diagonal \gls{ris} scales with forward and backward channel ranks.
		\end{subsubsection}

@@

	\begin{subsection}{Achievable Rate Maximization}
		\begin{figure}[!t]
			\centering
			\subfloat[$1 \times 256 \times 1$ (no direct)\label{fg:power_bond_txrx1_nd}]{
				\resizebox{0.4725\columnwidth}{!}{
					\input{assets/simulation/power_bond_txrx1_nd.tex}
				}
			}
			\subfloat[$4 \times 256 \times 4$ (no direct)\label{fg:power_bond_txrx4_nd}]{
				\resizebox{0.4875\columnwidth}{!}{
					\input{assets/simulation/power_bond_txrx4_nd.tex}
				}
			}
			\caption{
				Average channel power versus \gls{bd}-\gls{ris} group size and \gls{mimo} dimensions.
			}
			\label{fg:power_bond}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\subfloat[$4 \times N_\mathrm{S} \times 4$ (no direct)\label{fg:power_sx_txrx4_nd}]{
				\resizebox{0.49\columnwidth}{!}{
					\input{assets/simulation/power_sx_txrx4_nd.tex}
				}
			}
			\subfloat[$16 \times N_\mathrm{S} \times 16$\label{fg:power_sx_txrx16}]{
				\resizebox{0.47\columnwidth}{!}{
					\input{assets/simulation/power_sx_txrx16.tex}
				}
			}
			\caption{
				Average channel power versus antenna size and \gls{bd}-\gls{ris} group size.
			}
			\label{fg:power_sx}
		\end{figure}

>>>>

		\begin{corollary}[upper bound on the sum of first $k$ singular values to the power of $p$\label{co:sum_power}]
			\begin{equation}
				\sum_{n=1}^k \sigma_n^p(\mathbf{H}) \le \sum_{n=1}^k \sigma_n^p(\mathbf{H}_\mathrm{B}) \sigma_n^p(\mathbf{H}_\mathrm{F}), \quad p > 0.
				\label{iq:sv_bound_fc_power}
			\end{equation}
			When $k = N'$ and $p = 2$, \eqref{iq:sv_bound_fc_power} suggests the channel power is upper bounded by the sum of (sorted) element-wise power product of backward and forward subchannels.
		\end{corollary}

		\begin{remark}
			From \eqref{eq:scattering_fc} and \eqref{eq:channel_equivalent_fc} in the proof of Proposition \ref{pp:fully_connected}, we notice that \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
			% Interestingly, \eqref{iq:sv_bound_fc}--\eqref{iq:sv_bound_fc_power} are simultaneously tight when
			\begin{equation}
				\mathbf{\Theta} = \mathbf{V}_\mathrm{B} \mathbf{U}_\mathrm{F}^\mathsf{H}.
				\label{eq:scattering_fc_tight}
			\end{equation}
			An interpretation is that the off-diagonal entries can enhance the capabilities of
			\begin{itemize}
				\item subspace alignment: $\mathbf{V}_\mathrm{B}$ and $\mathbf{U}_\mathrm{F}^\mathsf{H}$ in \eqref{eq:scattering_fc} fully align the subspaces of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ by rotation;
				\item subchannel rearrangement: $\mathbf{X} = \mathbf{I}$ in \eqref{eq:channel_equivalent_fc} pairs the subchannels of $\mathbf{H}_\mathrm{B}$ and $\mathbf{H}_\mathrm{F}$ from strongest to weakest, which attains the maximal in rearrangement inequality.
			\end{itemize}
		\end{remark}

@@

		\begin{proposition}\label{pp:power}
			Starting from any $\mathbf{\Theta}^{(0)} \in \mathbb{U}^{N_\mathrm{S} \times N_\mathrm{S}}$, the sequence
			\begin{equation}
				\mathbf{\Theta}_g^{(r+1)} = \mathbf{U}_g^{(r)} \mathbf{V}_g^{(r)}, \quad \forall g
				\label{eq:scattering_power}
			\end{equation}
			converges to a stationary point of \eqref{op:power_passive}, where $\mathbf{U}_g^{(r)}$ and $\mathbf{V}_g^{(r)}$ are the left and right compact singular matrix of
			\begin{equation}
				\mathbf{M}_g^{(r)} = \mathbf{H}_{\mathrm{B},g}^\mathsf{H} \Bigl(\mathbf{H}_\mathrm{D} + \mathbf{H}_\mathrm{B} \mathrm{diag}\bigl(\mathbf{\Theta}_{[1:g-1]}^{(r+1)},\mathbf{\Theta}_{[g:G]}^{(r)}\bigr) \mathbf{H}_\mathrm{F}\Bigr) \mathbf{H}_{\mathrm{F},g}^\mathsf{H}
				\label{eq:auxiliary_matrix_power}
			\end{equation}
		\end{proposition}

@@

	\begin{subsection}{Channel Singular Values Redistribution}
		\begin{subsubsection}{Pareto Frontier}
			\begin{figure}[!t]
				\centering
				\subfloat[$2 \times 32 \times 2$ (no direct)\label{fg:singular_pareto_sx32_nd}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_pareto_sx32_nd.tex}
					}
				}
				\subfloat[$2 \times 32 \times 2$\label{fg:singular_pareto_sx32}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_pareto_sx32.tex}
					}
				}
				\\
				\subfloat[$2 \times 64 \times 2$\label{fg:singular_pareto_sx64}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_pareto_sx64.tex}
					}
				}
				\subfloat[$2 \times 128 \times 2$\label{fg:singular_pareto_sx128}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_pareto_sx128.tex}
					}
				}
				\caption{Pareto frontiers of singular values of a 2T2R channel reshaped by a \gls{ris}.}
				\label{fg:singular_pareto}
			\end{figure}
			% Fig. \ref{fg:singular_pareto} shows the Pareto frontiers of channel singular values reshaped by \gls{bd}-\gls{ris}.
			Fig. \ref{fg:singular_pareto} shows the Pareto singular values of a 2T2R \gls{mimo} reshaped by a \gls{ris}.
			When the direct link is absent, the achievable regions in Fig. \subref*{fg:singular_pareto_sx32_nd} are shaped like pizza slices.
			This is because $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$ and there exists a tradeoff between aligning the two subspaces.
			%  since $\sigma_1(\mathbf{H}) \ge \sigma_2(\mathbf{H}) \ge 0$.
			We observe that the smallest singular value is enhanced up to \num{2e-4} by diagonal \gls{ris} and \num{3e-4} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{50}{\percent} gain.
			When the direct link is present, the shape of the singular value region depends heavily on the relative strength of the indirect link.
			In Fig. \subref*{fg:singular_pareto_sx32}, a 32-element \gls{ris} is insufficient to compensate the \qty{35}{dB} path loss imbalance and results in a limited singular value region that is symmetric around the direct point.
			As the group size $L$ increases, the shape of the region evolves from elliptical to square.
			This transformation not only provides a better tradeoff in subchannel manipulation but also improves the dynamic range of $\sigma_1(\mathbf{H})$ and $\sigma_2(\mathbf{H})$ by \qty{22}{\percent} and \qty{38}{\percent}, respectively.
			The achievable singular value region also enlarges as the number of scattering elements $N_\mathrm{S}$ increases.
			In particular, Fig. \subref*{fg:singular_pareto_sx128} shows that the equivalent channel can be completely nulled by a 128-element \gls{bd}-\gls{ris} but not by a diagonal one.
			Those results demonstrate the superior channel shaping capability of \gls{bd}-\gls{ris} for better signal enhancement and interference suppression.
		\end{subsubsection}

		\begin{subsubsection}{Analytical Bounds and Numerical Results}
			\begin{figure}[!t]
				\centering
				\subfloat[$4 \times 32 \times 4$ (rank-1)\label{fg:singular_bound_rank1_sx32}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_bound_rank1_sx32.tex}
					}
				}
				\subfloat[$4 \times 64 \times 4$ (rank-1)\label{fg:singular_bound_rank1_sx64}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_bound_rank1_sx64.tex}
					}
				}
				\\
				\subfloat[$4 \times 128 \times 4$ (rank-2)\label{fg:singular_bound_rank2_sx128}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_bound_rank2_sx128.tex}
					}
				}
				\subfloat[$4 \times 256 \times 4$ (rank-4)\label{fg:singular_bound_rank4_sx256}]{
					\resizebox{0.48\columnwidth}{!}{
						\input{assets/simulation/singular_bound_rank4_sx256.tex}
					}
				}
				\caption{
					Achievable channel singular values: analytical bounds (green lines) and numerical optimization results (blue and red bars).
					`D' means diagonal \gls{ris} and `BD' means fully-connected \gls{bd}-\gls{ris}.
					`rank-$k$' refers to the forward channel.
				}
				\label{fg:singular_bound}
			\end{figure}
			Fig. \ref{fg:singular_bound} illustrates the analytical singular value bounds in Proposition \ref{pp:rank_deficient} and the numerical results obtained by solving problem \eqref{op:pareto} with $\rho_n = \pm 1$ and $\rho_{n'} = 0$, $\forall n' \ne n$.
			Here we assme a rank-$k$ forward channel without loss of generality.
			When the \gls{ris} is in the vicinity of the transmitter, Figs. \subref*{fg:singular_bound_rank1_sx32} and \subref*{fg:singular_bound_rank1_sx64} show that the achievable channel singular values indeed satisfy Corollary \ref{co:los}, namely $\sigma_1(\mathbf{H}) \ge \sigma_1(\mathbf{T})$, $\sigma_2(\mathbf{T}) \le \sigma_2(\mathbf{H}) \le \sigma_1(\mathbf{T})$, etc.
			It is obvious that \gls{bd}-\gls{ris} can approach those bounds better than diagonal \gls{ris} especially for a small $N_\mathrm{S}$.
			% Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} where the forward channel is rank-2.
			Another example is given in Fig. \subref*{fg:singular_bound_rank2_sx128} with rank-2 forward channel.
			% The observations align with Proposition \ref{pp:rank_deficient} that t
			The first two channel singular values are unbounded above and bounded below by the first two singular values of $\mathbf{T}$, while the last two singular values can be suppressed to zero and bounded above by the first two singular values of $\mathbf{T}$.
			Those observations align with Proposition \ref{pp:rank_deficient} and Corollary \ref{co:extreme}.
			Finally, Fig. \subref*{fg:singular_bound_rank4_sx256} confirms there are no extra singular value bounds when both forward and backward channels are full-rank.
			This can be predicted from \eqref{eq:auxiliary_matrix} where the compact singular matrix $\mathbf{V}_\mathrm{F}$ becomes unitary and $\mathbf{T}=\mathbf{0}$.
			The numerical results are consistent with the analytical bounds, and we conclude that the channel shaping advantage of \gls{bd}-\gls{ris} over diagonal \gls{ris} scales with forward and backward channel ranks.

			\begin{figure}[!t]
				\centering
				\subfloat[$1 \times 256 \times 1$ (no direct)\label{fg:power_bond_txrx1_nd}]{
					\resizebox{0.4725\columnwidth}{!}{
						\input{assets/simulation/power_bond_txrx1_nd.tex}
					}
				}
				\subfloat[$4 \times 256 \times 4$ (no direct)\label{fg:power_bond_txrx4_nd}]{
					\resizebox{0.4875\columnwidth}{!}{
						\input{assets/simulation/power_bond_txrx4_nd.tex}
					}
				}
				\caption{
					Average maximum channel power versus \gls{bd}-\gls{ris} group size and \gls{mimo} dimensions.
					`Cascaded' refers to the available power of the cascaded channel, i.e., the sum of (sorted) element-wise power product of backward and forward subchannels.
				}
				\label{fg:power_bond}
			\end{figure}

			Fig. \ref{fg:power_bond} compares the analytical channel power bound in Corollary \ref{co:sum_power} with $k=N'$, $p=2$ and the numerical results obtained by solving problem \eqref{op:power_passive} when the direct link is absent.
			Here, a fully-connected \gls{bd}-\gls{ris} can attain the upper bound either in closed form \eqref{eq:scattering_fc_tight} or via optimization approach \eqref{eq:scattering_power}.
			% Recall that a fully-connected \gls{bd}-\gls{ris} in closed form \eqref{eq:scattering_fc_tight} can attain the bound.
			% We observe that the bound is also tight for fully-connected \gls{bd}-\gls{ris}.
			% Increasing the group size of \gls{bd}-\gls{ris} significantly improves the channel power especially for a large \gls{mimo}.
			% Apparently, \gls{bd}-\gls{ris} with a larger group size can approach the bound better, and a fully-connected one can achieve the bound.
			% The bound here indicates how much power can potentially be extracted from the forward and backward channels.
			% We observe that using a larger group size can approach the bound better, and full
			% We observe that the bound is tight for fully-connected \gls{bd}-\gls{ris} in \gls{siso} and \gls{mimo}.
			For the \gls{siso} case in Fig. \subref*{fg:power_bond_txrx1_nd}, the maximum channel power is approximately \num{4e-6} by diagonal \gls{ris} and \num{6.5e-6} by fully-connected \gls{bd}-\gls{ris}, corresponding to a \qty{62.5}{\percent} gain.
			This aligns with the asymptotic \gls{bd}-\gls{ris} scaling law derived for \gls{siso} in \cite{Shen2020a}.
			Interestingly, the gain surges to \qty{270}{\percent} in 4T4R \gls{mimo} as shown in Fig. \subref*{fg:power_bond_txrx4_nd}.
			This is because subspace alignment boils down to phase matching in \gls{siso} such that both triangular and Cauchy-Schwarz inequalities in \cite[(50)]{Shen2020a} can be simultaneously tight regardless of the group size.
			That is, diagonal \gls{ris} is sufficient for subspace alignment in \gls{siso} while the \qty{62.5}{\percent} gain from \gls{bd}-\gls{ris} comes purely from subchannel rearrangement (i.e., pairing the forward and backward channels from strongest to weakest).
			Now consider a diagonal \gls{ris} in \gls{mimo}.
			Each element can only apply a common phase shift to the associated rank-1 $N_\mathrm{R} \times N_\mathrm{T}$ indirect channel.
			Therefore, perfect subspace alignment of indirect channels through different elements is generally impossible.
			It means the disadvantage of diagonal \gls{ris} in subspace alignment and subchannel rearrangement scales with \gls{mimo} dimensions.
			We thus conclude that the power gain of \gls{bd}-\gls{ris} scales with group size and \gls{mimo} dimensions.
		\end{subsubsection}

@@

	\begin{subsection}{Achievable Rate Maximization}
		\begin{figure}[!t]
			\centering
			\subfloat[$4 \times N_\mathrm{S} \times 4$ (no direct)\label{fg:power_sx_txrx4_nd}]{
				\resizebox{0.49\columnwidth}{!}{
					\input{assets/simulation/power_sx_txrx4_nd.tex}
				}
			}
			\subfloat[$16 \times N_\mathrm{S} \times 16$\label{fg:power_sx_txrx16}]{
				\resizebox{0.47\columnwidth}{!}{
					\input{assets/simulation/power_sx_txrx16.tex}
				}
			}
			\caption{
				Average channel power versus antenna size and \gls{bd}-\gls{ris} group size.
			}
			\label{fg:power_sx}
		\end{figure}
